---
title: "How to use the functions in this package - An example"
author: "Zhengguo"
date: "1/27/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

load("RnaDna.Rdata")
```

Here we perform a joint analysis on the RNA and DNA data from the dataset. 
## Data pre-preprocessing 
```{r}
DNA_data <- RnaDna[[1]]
dim(DNA_data)
RNA_data <- RnaDna[[2]]
dim(RNA_data)
```
Note that the DNA and RNA datasets share the same subjects (44 rows). The datasets must be standardized.
```{r}
DNA_s <- mySTD(DNA_data)
RNA_s <- mySTD(RNA_data)
```
 
## Some exploratory analysis
We first use `VAF()` to explore the data. Note that `VAF()` use the concatenated data as the input. 
```{r}
concate_d <- cbind(DNA_s, RNA_s)
dim(concate_d)
Jk <- c(ncol(DNA_s), ncol(RNA_s))
Jk

VAF(concate_d, Jk, R=30)
```
Because we do not know how many components there are in the concatenated data, we can try different numbers. Here is an example of 30 components. It seems that in the DNA block there is no dominating component, but in the RNA block, there is a dominating component (the first component). 

